---
title: "WOF Analysis"
output: html_notebook
---

making list of all clues - do once & save as csv
```{r}
library(rvest)
library(dplyr)

url <- "https://buyavowel.boards.net/page/compendium30"
webpage <- read_html(url)

table <- webpage %>%
  html_node("table") %>%
  html_table(fill = TRUE)

# Convert to a data frame
prize_data <- as.data.frame(table)
prize_data <- prize_data[7:nrow(prize_data),1:5]

# Rename columns for clarity (adjust based on actual table headers)
colnames(prize_data) <- c("Puzzle", "Category", "Date", "Episode_Number", "Round")


scrape_pages <- function(num, full_set){
  url <- paste("https://buyavowel.boards.net/page/compendium", num, sep = "")
  webpage <- read_html(url)

  # Find the table on the page
  table <- webpage %>%
    html_node("table") %>%
    html_table(fill = TRUE)
  
  # Convert to a data frame
  ddd <- as.data.frame(table)
  ddd <- ddd[7:nrow(ddd),1:5]
  
  # Rename columns for clarity (adjust based on actual table headers)
  colnames(ddd) <- c("Puzzle", "Category", "Date", "Episode_Number", "Round")
  
  full_set <- rbind(full_set, ddd)
  return(full_set)
  paste("did season ", num)
}

for(i in 32:42){
  prize_data <- scrape_pages(i, prize_data)
}

```

start here
```{r}
library(tidyverse)
library(tidyr)
library(dplyr)
library(stopwords)
data <- read.csv("all_recent_puzzles.csv", as.is=T)
data <- data %>%
  filter(Puzzle != "")

words <- data %>%
  separate_rows(Puzzle, sep = " ") %>%
  mutate(Puzzle = trimws(Puzzle)) %>%
  filter(Puzzle != "") %>%
  mutate(Puzzle = tolower(Puzzle))
```

word and category frequency
```{r}
# Count the frequency of each word
full_counts <- words %>%
  count(Puzzle, sort = TRUE)

category_counts <- data %>%
  mutate(Category = if_else(str_detect(Round, "\\^"), "Crossword", Category)) %>%
  count(Category, sort = TRUE)

```

get common words in each category
```{r}
get_most_common_words <- function(dat, cat) {
  # Count the frequency of each word
  word_counts <- dat %>%
    filter(Category == cat) %>%
    count(Puzzle, sort = TRUE)

  return(word_counts)
}

head(get_most_common_words(words, "Phrase"), 20)
head(get_most_common_words(words, "What Are You Doing?"), 30)
head(get_most_common_words(words, "Food & Drink"), 20)
head(get_most_common_words(words, "Place"), 30)
head(get_most_common_words(words, "Fun & Games"), 20)
head(get_most_common_words(words, "Event"), 20)
head(get_most_common_words(words, "Living Thing"), 20)
head(get_most_common_words(words, "Living Things"), 20)
head(get_most_common_words(words, "Event"), 20)
head(get_most_common_words(words, "Person"), 20)

```

letter frequency, both overall and in bonus round
```{r}
all_letters <- words %>%
  separate_rows(Puzzle, sep = "") %>%
  filter(Puzzle != "")

# overall
letter_counts <- all_letters %>%
  count(Puzzle, sort = TRUE)

# in bonus round, removing the ones they give you
bonus_letter_counts <- all_letters %>%
  filter(grepl("BR", Round)) %>%
  filter(Puzzle != "r" ) %>%
  filter(Puzzle != "s" ) %>%
  filter(Puzzle != "t" ) %>%
  filter(Puzzle != "l" ) %>%
  filter(Puzzle != "n" ) %>%
  filter(Puzzle != "e" ) %>%
  count(Puzzle, sort = TRUE)
  
  
  #c("r", "s", "t", "l", "n", "e")


```

little words and apostrophes
```{r}
two_letter <- full_counts %>%
  filter(str_length(Puzzle) == 2)

three_letter <- full_counts %>%
  filter(str_length(Puzzle) == 3)

apos <- full_counts %>% 
  filter(grepl("'", Puzzle))
  

```

_R
```{r}
words_with_r <- words %>%
  filter(substr(Puzzle, 2, 2) == "r")  # Check if the 2nd letter is "R"

common_r <- words_with_r %>%
  count(Puzzle, sort = TRUE)

before_r <- words_with_r %>%
  mutate(first_letter = substr(Puzzle, 1, 1)) %>%  
  count(first_letter, sort = TRUE)

```

_L
```{r}
words_with_l <- words %>%
  filter(substr(Puzzle, 2, 2) == "l")  

before_l <- words_with_l %>%
  mutate(first_letter = substr(Puzzle, 1, 1)) %>%  
  count(first_letter, sort = TRUE)

```

_H
```{r}
words_with_h <- words %>%
  filter(substr(Puzzle, 2, 2) == "h")  %>%
  filter(Puzzle != "the")

before_h <- words_with_h %>%
  mutate(first_letter = substr(Puzzle, 1, 1)) %>%  
  count(first_letter, sort = TRUE)

```

_P
```{r}
words_with_p <- words %>%
  filter(substr(Puzzle, 2, 2) == "p")  

before_p <- words_with_p %>%
  mutate(first_letter = substr(Puzzle, 1, 1)) %>%  
  count(first_letter, sort = TRUE)

```

_S (all vowels)
```{r}
words_with_s <- words %>%
  filter(substr(Puzzle, 2, 2) == "s")  

before_s <- words_with_s %>%
  mutate(first_letter = substr(Puzzle, 1, 1)) %>%  
  count(first_letter, sort = TRUE)

```

_T
```{r}
words_with_t <- words %>%
  filter(substr(Puzzle, 2, 2) == "t")  

before_t <- words_with_t %>%
  mutate(first_letter = substr(Puzzle, 1, 1)) %>%  
  count(first_letter, sort = TRUE)

```

_N (all vowels)
```{r}
words_with_n <- words %>%
  filter(substr(Puzzle, 2, 2) == "n")  

before_n <- words_with_n %>%
  mutate(first_letter = substr(Puzzle, 1, 1)) %>%  
  count(first_letter, sort = TRUE)

```

end of word patterns
```{r}
end_ne <- words %>%
  mutate(Puzzle = str_trim(Puzzle)) %>%
  filter(str_detect(Puzzle, "ne$")) %>%
  count(Puzzle, sort = TRUE)

end_le <- words %>%
  mutate(Puzzle = str_trim(Puzzle)) %>%
  filter(str_detect(Puzzle, "le$")) %>%
  count(Puzzle, sort = TRUE)

end_l <- words %>%
  mutate(Puzzle = str_trim(Puzzle)) %>%
  filter(str_detect(Puzzle, "l$")) %>%
  count(Puzzle, sort = TRUE)

end_t <- words %>%
  mutate(Puzzle = str_trim(Puzzle)) %>%
  filter(str_detect(Puzzle, "t$")) %>%
  count(Puzzle, sort = TRUE)

end_te <- words %>%
  mutate(Puzzle = str_trim(Puzzle)) %>%
  filter(str_detect(Puzzle, "te$")) %>%
  count(Puzzle, sort = TRUE)

end_n <- words %>%
  mutate(Puzzle = str_trim(Puzzle)) %>%
  filter(str_detect(Puzzle, "n$")) %>%
  count(Puzzle, sort = TRUE)

```

analyzing frequency prize puzzle categories and clues
```{r}
all_prize_puzzles <- data %>%
  filter(grepl("\\*", Round)) %>%
  select(Puzzle, Category)
  
prize_category_frequency <- all_prize_puzzles %>%
  count(Category, sort = TRUE) %>%
  rename(Frequency = n)

prize_word_frequency <- all_prize_puzzles %>%
  mutate(Puzzle = tolower(Puzzle)) %>%   
  unnest_tokens(word, Puzzle) %>%       
  count(word, sort = TRUE) %>%          
  rename(Frequency = n)

```

analyzing bonus round clues
```{r}
all_bonus_puzzles <- data %>%
  filter(grepl("BR", Round)) 

# word frequency
bonus_word_frequency <- all_bonus_puzzles %>%
  mutate(Puzzle = tolower(Puzzle)) %>%   
  unnest_tokens(word, Puzzle) %>%       
  count(word, sort = TRUE) %>%          
  rename(Frequency = n)

# character frequency
bonus_letter_frequency <- all_bonus_puzzles %>%
  mutate(Puzzle = tolower(Puzzle)) %>%   
  unnest_tokens(letter, Puzzle, token = "characters") %>%
  count(letter, sort = TRUE) %>%          
  rename(Frequency = n) %>%
  mutate(Given = ifelse(letter %in% c("r", "s", "t", "l", "n", "e"), 1, 0))

```

most common words starting with each letter
```{r}
get_words_by_letter <- function(let) {
  these_words <- words %>%
    filter(substr(Puzzle, 1, 1) == let)  %>%
    count(Puzzle, sort = TRUE) %>%
    rename(Frequency = n) %>%
    head(15)
  
  return(these_words)
}

popular_by_letter <- get_words_by_letter("a")
for(i in 2:26){
  popular_by_letter <- rbind(popular_by_letter, get_words_by_letter(letters[i]))
}

popular_words <- popular_by_letter %>%
  filter(Frequency >= 30)

popular_words_full <- words %>%
  filter(Puzzle %in% popular_words$Puzzle) %>%
  filter(str_length(Puzzle) >= 4) %>%
    mutate(Puzzle = toupper(Puzzle))
  
```

words with certain letter in certain spot
```{r}
popular_by_letter %>%
  filter(substr(Puzzle, 3, 3) == "t")

```

looking through triple toss-ups
```{r}
triples <- data %>%
  filter(as.Date(Date, format="%m/%d/%y") >= as.Date("9/9/19", format="%m/%d/%y")) %>%
  filter(grepl("\\T[3,4,5]", Round)) 


```

save top 15 words as as phone wallpapers
```{r}
library(magick)
library(RColorBrewer)
## use popular_by_letter

# Set parameters for the image
width <- 1080          # Width of the image (in pixels)
height <- 1920         # Height of the image (in pixels)
text_color <- "black"       # Text color
font_size <- 75             

write_wallpapers <- function(i, my_data){
 if(i==24) return("no")
  let <- letters[i]
  background_color <- brewer.pal(12, "Set3")[i %% 12 + 1]
  
  output_path <- paste("wallpaper_", let, ".png", sep="")
  chosen_words <- my_data %>% 
    filter(substr(Puzzle, 1, 1) == let) 
  text <- paste(chosen_words$Puzzle, collapse = "\n")
  
  # Create a blank image with the specified background color
  image <- image_blank(width = width, height = height, color = background_color)
  
  # Annotate the image with the text
  image <- image_annotate(
    image,
    text = text,
    color = text_color,
    size = font_size,
    gravity = "center",
    location = "+0+120"
  )

  image_write(image, output_path)
  
}

for(i in 1:26){
  write_wallpapers(i, popular_by_letter)
}

write_wallpapers(1, popular_by_letter)

```

estimating the bonus round wedge distribution
```{r}
library(rvest)
library(stringr)
library(dplyr)

# gathering links of game write-ups
url <- "https://buyavowel.boards.net/thread/19071/season-40-recap-directory"
page <- read_html(url)

links <- as.data.frame(page %>%
  html_nodes("a") %>%          
  html_attr("href"))

names(links)[1] <- "URLs" 

filtered_links <- links %>%
  filter(grepl("^https://buyavowel.boards.net/thread", URLs)) %>%
  filter(!grepl("cwof", URLs)) # celeb WOF has diff wedges

##############################################################
# Function to extract the bonus round prize from a single page
extract_prize <- function(i) {
  my_url <- filtered_links$URLs[i]
  page <- tryCatch(read_html(my_url), error = function(e) NULL)
  if (is.null(page)) {
    return(NA)
  }

  bonus_round_section <- page %>%
      html_nodes("body") %>%      
      html_text(trim = TRUE) %>%  
      str_split("BONUS ROUND") %>%  # Split at the "BONUS ROUND" section
      .[[1]]
  
  #take last entry
  bonus_round_section <- bonus_round_section[length(bonus_round_section)]
  
 prize_text <- bonus_round_section %>%
    str_extract(".+?(?=\n\t\t\t\t\t\t\n)") %>% # stop before comment section
    tolower()
  
  ## looking for cash or car options
  cash_options <- c("40,000|45,000|50,000|75,000|100,000|1,000,000")
  car_options <- c("car|ford|bmw|mini cooper|toyota|mazda|honda|mercedes|infiniti|chevy|lincoln|nissan")

  cash_match <- str_extract_all(prize_text, cash_options)[[1]]
  car_match <- car_options[str_detect(prize_text, car_options)]
  
  if(length(cash_match) == 1) return(cash_match)
  if(length(car_match) > 0) return("car")
  if(length(cash_match) >= 2) return ("too much cash")
  if(length(car_match) == 0 & length(cash_match) == 0) return("both missing")
}

# making list of prizes
bonus_prizes <- as.data.frame(filtered_links)
bonus_prizes$Prize <- "NA"
for(i in 1:nrow(bonus_prizes)){
  bonus_prizes$Prize[i] <- extract_prize(i)
}
#manual fixes
bonus_prizes$Prize[55] <- "40,000"
bonus_prizes$Prize[70] <- "50,000"
bonus_prizes$Prize[172] <- "40,000"
bonus_prizes$Prize[187] <- "40,000"
bonus_prizes$Prize[191] <- "40,000"

# analyzing the results
bonus_results <- bonus_prizes %>%
  group_by(Prize) %>%                 
  summarise(count = n()) %>%          
  mutate(Percentage = round(count / sum(count) * 100, 1))

```

retrospective of my game
```{r}
# H = bad guess
words %>%
  filter(substr(Puzzle, 1, 1) == "t") %>%
  filter(substr(Puzzle, 2, 2) == "h") %>%
  filter(substr(Puzzle, 4, 4) == "e") %>%
  filter(nchar(Puzzle) == 4)

# C = another bad guess. it didn't matter! 
words %>%
  filter(substr(Puzzle, 1, 1) == "t") %>%
  filter(substr(Puzzle, 3, 3) == "c") %>%
  filter(substr(Puzzle, 4, 4) == "e") %>%
  filter(nchar(Puzzle) == 4)

```

